%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Projects/Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    
%---------------------------------------------------------
  \cventry
    {Summer Research Intern} % Job title
    {Cryptology Division, Indian Statistical Institute (Prof. Subhamoy Maitra)} % Organization
    {Kolkata, India} % Location
    {May - July 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of recognizing patterns in weak states of RC4 stream cipher.}
        \item {Implemented a technique to identify possible set of states that resemble \textbf{Finney States}.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Title: Extending PRES+ based Equivalence Checking for parallel behaviour} % Job title
    {Bachelor Thesis, IIT Kharagpur (Prof. Dipankar Sarkar \& Prof. Chittaranjan Mandal)} % Organization
    {Kharagpur, India} % Location
    {August 2011 - April 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formulated behavioural models of real-time systems using \textbf{PRES+} and \textbf{Timed FSMD} to verify timing properties and path-based equivalence.}
        \item {As a real-life example, modeled an Adaptive Cruise Control mechanism using the same verification scheme.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Job title
    {Notable Academic Summer/Term Projects (IIT Kharagpur)} % Organization
    {Kharagpur, India} % Location
    {} % Date(s)
    { \vspace{-5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Successfully performed \textbf{DPA} (Differential Power Analysis - a variation of Side Channel Attack) on DES using \textbf{SASEBO} (Side-Channel Attack Evaluation Board). Used Xilinx 7.1 and implemented the algorithms in Verilog. Also optimized \textbf{SPA} (Simple Power Analysis) for RSA. This was done during summer break, May-June, 2009 and winter recess, December, 2009 under Prof. Debdeep Mukhopadhyay, IIT KGP.}
        \item {Implemented a Recommendation engine to suggest \textbf{Friend in a social network}, as a part of Machine Learning course. Designed the problem as a Classification Problem, and applied Rank Heuristics to train a SVM classifier.}
        \item {Build a Dynamic Large Polygonal Mess Renderer and Editor (taking .ply or .obj files as input) using C++ and GLUT (OpenGL Utility Toolkit) as part of Computational Graphics Course. Added a functionality of 3D Convex Hull Computation and rendering and applied significant optimizations.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
