%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Architect} % Job title
    {GoZoomo.com} % Organization
    {Bangalore, India} % Location
    {September 2014 - Present} % Date(s)	
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As the \textbf{founding engineer}, was responsible to design, develop and deliver full-stack end-to-end solutions for the business from scratch, building and maintaining the infrastructure in cloud, leading critical projects, growing the tech team and contribute to overall company vision as a founding core team member.}
        \item {Notable technical achievements:}
        \begin{itemize}
         \item {Engineered Whatsapp client using \textbf{Python} for lead platform, effecting 10x buyer liquidity for customer acquisition team.}
         \item {Developed a scraping engine using \textbf{Clojure} to collect and analyze legitimate seller leads from web; resulting 10x growth of seller liquidity.}
         \item {Developed a scalable and asynchronous notification system using \textbf{RabbitMQ} and Clojure, resulting fast and rapid delivery of bulk notification including SMS, Email and Push Notification.}
         \item {Developed desktop and mobile websites (\textbf{AngularJS} and \textbf{Twitter Bootstrap} for client side, \textbf{Erlang} for REST APIs and back-end) of GoZoomo, able to serve up to 600k requests per minute. Re-wrote parts of Erlang driver for MongoDB.}
         \item {Led the inception and design of seller portal, causing huge boost to seller-buyer interaction and pricing correction. It was developed in Java and used non-blocking \textbf{Undertow} connections.}
         \item {Introduced \textbf{Thrift} in GoZoomo, providing an unified and validating interface for micro-services used internally.}
        \end{itemize}
        \item {Designed micro-services architecture of GoZoomo stack; led the DevOps team, development of infra and CI/CD in AWS for entire stack.}
        \item {Periodically took technical interviews for recruitment into tech team; mentored and inspired juniors.}
        \item {As a result, the company ensured Series A funding, and was appreciated by the CTO in subsequent appraisal rounds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {BankBazaar.com} % Organization
    {Bangalore, India} % Location
    {June 2012 - August 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full-stack development on several channels for BankBazaar.com marketplace and other Whitelabels.}
        \item {Key achievements:}
        \begin{itemize}
         \item {Pioneered development of integration web-services (REST/SOAP/RMI) with the most prominent banks in India (\textbf{ICICI/HDFC/CITI} etc.), resulting recurring faster roll-out and integration of new and existing channels. Was made primary owner of the same.}
         \item {Was made lead developer and primary owner of internal web service in \textbf{Clojure} responsible for dynamic content generation.}
         \item {Built a \textbf{SSO(Single Sign On)} solution for Pre-approved Offers product by ICICI bank using \textbf{OpenSAML}, causing increased Credit Card and Home Loan conversions. This has proved to be one of the best products for BankBazaar and ICICI in the long run.}
         \item {Built v1 of BankBazaar marketplace onboarding flow, causing 4x conversions and later was adopted by all such flows in marketplace.}
         \item {Closely involved in infrastructural growth involving physical machines, cloud, maintenance, DevOps and reporting. Mostly used \textbf{SaltStack}, Python and shell scripts. Have led many severe security issue mitigation sessions with minimum TAT.}
        \end{itemize}
        \item {Was promoted to code reviewer and charged with end-to-end project responsibility within 5 months of joining as a fresher.}
        \item {As recognition of exemplary performance, was awarded \textbf{highest promotional rating} in appraisal.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {IBM Extreme Blue Program (IBM India Software Labs)} % Organization
    {Bangalore, India} % Location
    {May - July 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Project title}: Efficient Collaborative Decision Making with Mobility; \textbf{Client}: Mumbai Airport Authority}
        \item {\textbf{Project objective}: To design a low cost mobile solution for managing complex hierarchical decision tasks in reduced visibility condition}
        \item {Successfully built a proof-of-concept Airport CDM mobile platform implementation with low network bandwidth usage.}
        \item {Used JQuery mobile and HTML5 Web SQL for front-end and Java, Websphere Mobility Pack, DB2 and Websphere MQ for back-end.}
        \item {The solution developed was projected to have a Cost-to-benefit ratio of \textbf{1:9} and expected break-even of \textbf{2 years}. Based on the stats, technology was transferred to a IBM developer team for full and end-to-end development.}
        \item {Was awarded \textbf{Pre-placement Offer} from IBM for excellent performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
