%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web and Systems Team Head, Problems Team member} % Affiliation/role
    {Bitwise, Algorithmic Programming Contest, CSE Dept, IIT KGP} % Organization/group
    {IIT Kharagpur} % Location
    {2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built the website for Bitwise 2012 and Enigma using PHP. Added several enhancements e.g. monitoring, ticker, better submission interface.}
        \item {Built an Online Judge capable of evaluating C/C++/Java/Python code against sample test-cases and update results and leaderboard.}
        \item {Contributed algorithmic problems for contest set. The optimum difficulties and tricks made the contest a huge success.}
        \item {Co-ordinated PR for the event, resulting top participants from around the world e.g.\textit{Tourist, Rudy} etc. Facebook and Google were title sponsors.}
        \item {As an added responsibility, managed security and mail servers of CSE Department for the entire year.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Coordinator} % Affiliation/role
    {Overnite Programming Contest, endorsed by ACM ICPC and Kshitij, Tech Fest, IIT KGP} % Organization/group
    {IIT Kharagpur} % Location
    {September 2010 - January 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed contest problems for over 3000 participants in knockout round and 25 finalists.}
        \item {Built online judge using Django, implemented a distributed system (celery as message broker) to evaluate submissions using multiple workers.}
        \item {Compliance with ACM rules and smooth co-ordination earned praise from the fest management and ACM as well.}
      \end{cvitems}
    }    
    
%---------------------------------------------------------
  \cventry
    {Captain, Rajendra Prasad Hall of Residence} % Affiliation/role
    {Opensoft Competition, Technology General Championship} % Organization/group
    {IIT Kharagpur} % Location
    {July 2011 - April 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was responsible for leading RP Hall team in Opensoft event, Tech GC. Led a team of 15-something students.}
        \item {Designed and implemented a cross-platform voice-controlled file browser for the disabled as problem statement.}
        \item {Mostly used Python for designing GUI. CMU Sphinx was used for voice processing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Captain, Rajendra Prasad Hall of Residence} % Affiliation/role
    {Product Design Competition, Innovation Cup, Technology General Championship} % Organization/group
    {IIT Kharagpur} % Location
    {July 2011 - April 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {As recognition of success in previous year, was made captain for the same event. Led a team of 10 students.}
        \item {Designed a Condensing Steam Turbine Generator consuming biomass fuel as problem statement.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
